Andres Karjus

### 2021-10-28 index.Rmd
news

- My postdoc does not include teaching activities, but I do occasional guest lectures; most recently for the Data Science and Digital Humanities programme at the University of Tartu and for the Cultural Data Analytics I course at Tallinn University.

>>>>

- My postdoc includes some teaching activities, and I do occasional guest lectures; most recently for the Data Science and Digital Humanities programme at the University of Tartu and for the Cultural Data Analytics I and II courses at Tallinn University.
